### 2017-05-13 paper/evaluation.tex
Updated table and ordered by name

\begin{figure*}[t]  
\centering
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Jankotek MapDB  & \entry{8.2m}{5,324} & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%

@@

AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{}{} & \entry{}{}\\%

@@

Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\

RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\

JCabi Github                  & \entry{2.6m}{634} & \entry{2.1x}{0\%} & \entry{17.7x}{0\%} & \entry{28.8x}{0\%} & \entry{}{} & \entry{}{} \\

	Moquette & \entry{3.5m}{x} & \entry{4.2x}{x} & \entry{2.9x}{} & \entry{13.5x}{} & \entry{}{} & \entry{}{} \\

>>>>

\begin{figure*}[t]  
\centering
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%

@@

@@

Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\ 
JCabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{}{} & \entry{}{} \\
JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{}{} & \entry{}{}\\%
MapDB  & \entry{8.2m}{5,324}  & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
Moquette                      & \entry{3.7m}{169} & \entry{4.62x}{65.64\%} & \entry{3.36x}{32.92\%} & \entry{12.33x}{77.78\%} & \entry{}{} & \entry{}{} \\
RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\
Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%
